\documentclass[overlapped,line]{res}
\usepackage{ifpdf}
\usepackage{verbatim}
\usepackage{natbib}
\usepackage{bibentry}
\usepackage{etaremune}
%\usepackage{harvard}

\nobibliography*


%%===========================================================================%%

\begin{document}

%---------------------------------------------------------------------------
% Document Specific Customizations

% Make lists without bullets and with no indentation
\setlength{\leftmargini}{0em}
\renewcommand{\labelitemi}{}

% Use large bold font for printed name at top of pages
\renewcommand{\namefont}{\large\textbf}

% Make a nicer C++
\def\Cplusplus{C{\raise.5ex\hbox{\footnotesize ++ }}}

%---------------------------------------------------------------------------

\name{Bruce A. Desmarais~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~Curriculum Vitae}

\begin{resume}

\begin{ncolumn}{2}
  Department of Political Science       &  \texttt{bdesmarais@psu.edu}  \\
  Pennsylvania State University  &  \texttt{brucedesmarais.com}  \\
  321 Pond Lab    &  \texttt{orcid.org/0000-0002-3031-8883} \\ 
University Park, PA 16802 &  \texttt{linkedin.com/in/bruce-desmarais/} \\
 Phone: (814)863-8346  & \url{twitter.com/brucedesmarais}   \\  



\end{ncolumn}

%---------------------------------------------------------------------------

\section{\bf Employment}
\begin{itemize}
\item Professor, Department of Political Science and Institute for Computational and Data Sciences,  Pennsylvania State University. 2020--Present.
\item DeGrandis-McCourtney Early Career Professor in Political Science. 2018--Present.
\item Research Scientist, Core Data Science, Meta Platforms (Jan-Aug 2022, on sabbatical).
\item Associate Professor of Political Science, Pennsylvania State University. 2015--2020.
\item Assistant Professor of Political Science, University of Massachusetts Amherst. 2010--2015.
\end{itemize}

\section{\bf Affiliations}
\begin{itemize}
\item Director, Center for Social Data Analytics, Pennsylvania State University, Fall 2022--Present
\item Associate Director, Center for Social Data Analytics, Pennsylvania State University, Fall 2018--Spring 2022
\item Director of Graduate Studies, Programs in Social Data Analytics, Pennsylvania State University, Fall 2017--Present
\item Faculty Affiliate, Pennsylvania State University Institute for Computational and Data Sciences, Fall 2015--Present.
\item Visiting Fellow, Statistical and Applied Mathematical Sciences Institute (Research Triangle Park, NC), Fall 2013.
\item Faculty Affiliate, UMass Amherst Computational Social Science Initiative, Fall 2010 -- Spring 2015.
\item Associate Director, Institute for Social Science Research, University of Massachusetts Amherst, Spring 2014 -- Spring 2015.
\end{itemize}

\section{\bf Education}
\begin{itemize} 
\item Ph.D. Political Science, University of North Carolina at Chapel Hill, 2010\\
Specialties: Research Methods and American Politics
\item M.A. Political Science, University of North Carolina at Chapel Hill, 2008

\item B.A. Mathematical Economics and Public Policy, Eastern Connecticut State University, 2005,
\\ {\it Summa Cum Laude}
\end{itemize}
%---------------------------------------------------------------------------

%---------------------------------------------------------------------------

%------------------------------------------------------------------------------



%%==========================================================================

\section{\bf Publications}
\vspace{.1cm}
%\hspace{-1cm} \emph{Books}
%\begin{etaremune}
%\item Skyler J. Cranmer, Bruce A. Desmarais, and Jason Morgan. {\em Inferential Network Analysis}. Cambridge University Press. (Under Contract)
%\end{etaremune}
%\vspace{-.1cm}
\hspace{-1cm} \emph{Book} 
\begin{etaremune}
\item \bibentry{cranmer2020inferential}
\end{etaremune}
\vspace{.1cm}
\hspace{-1cm} \emph{Journal Articles}
\begin{etaremune}
\item \bibentry{fyfe2024isq}
\item \bibentry{TaiJITP}
\item \bibentry{gopalPSRM}
\item \bibentry{BoehmkeSDATA}
\item \bibentry{MedhaPA}
\item \bibentry{hardenJOP}
\item \bibentry{young2022}
\item \bibentry{KimPSRM}
\item \bibentry{KimLSQ}
\item \bibentry{NeumannJITP}
\item \bibentry{schmidPA2021}
\item \bibentry{schoeneman_zhu_desmarais_2020}
\item \bibentry{linder2020text}
\item \bibentry{boehmke2020spid}
\item \bibentry{cranmer2020contagion}
\item \bibentry{liu2019migration}
\item \bibentry{Scogin2019modeLLtest}
\item \bibentry{desmarais2019}
\item \bibentry{stillman2019consistent}
\item \bibentry{bergner}
\item \bibentry{phadke2018}
\item \bibentry{costa2019public}
\item \bibentry{bhamidi2018weighted}
\item \bibentry{Desmarais2018}
\item \bibentry{Bowers2018}
\item \bibentry{Stillman2017}
\item \bibentry{LeifeldJSS}
\item \bibentry{cranmer2017can}
\item \bibentry{Wilson:2017}
\item \bibentry{boehmke2017seeds}
\item \bibentry{ben2017transparency}
\item \bibentry{cranmer2016critique}
\item \bibentry{CostaRPR}
\item \bibentry{DesmaraisAPSR}
\item \bibentry{DesmaraisSoN}
\item \bibentry{DesmaraisAJPS}
\item \bibentry{Desmarais:2014}
\item \bibentry{Desmarais:2013qq}
\item \bibentry{Desmarais:2013}
\item \bibentry{Cranmer:2014son}
\item \bibentry{DesmaraisPSJ}. 
\item \bibentry{Cranmer:2012ii}
\item \bibentry{Benjamin:2012}.
\item \bibentry{Cranmer:2011cmps}.
\item \bibentry{Desmarais:2011pa}.
\item \bibentry{Desmarais:2011plos}. 
\item \bibentry{Desmarais:2012}.
\item \bibentry{Desmarais:2011physa}.
\item \bibentry{Cranmer:2011}. 
\item \bibentry{Harden:2011}
\item \bibentry{Freeman:2011}
\end{etaremune}

%\newpage

\hspace{-1cm} \emph{Peer Refereed Proceedings} 
\vspace{.1cm}
\begin{etaremune}
\item \bibentry{biswas2024political}
\item \bibentry{Xu2020}
\item \bibentry{kim2020effects}
\item \bibentry{desmarais2020policy} 
\item \bibentry{Marple2017}
\item \bibentry{schmid2017}
\item \bibentry{Krafft:2012}
\item \bibentry{Desmarais:2011ieee}. 
\item \bibentry{Desmarais:2010}. 
\end{etaremune}

\hspace{-1cm} \emph{Chapters in Edited Volumes} 
\vspace{.1cm}
\begin{etaremune}
\item \bibentry{gopal2023chapter}
\item \bibentry{schoenemanchapter}
\item \bibentry{desmarais2017statistical}
\end{etaremune}

\bibliographystyle{plain}
\nobibliography{vitabib.bib}


\renewcommand{\labelitemi}{\bf --}



\section{\bf Software}
\vspace{.4cm}
\begin{etaremune}
\item \bibentry{modeLLtest}
\item \bibentry{networkinference}
\item \bibentry{gergm}
\item \bibentry{xergm}
\end{etaremune}


\section{\bf Presentations}
\vspace{.1cm}
\hspace{-1cm} \emph{Invited Talks}
\begin{etaremune} 
\item ``Causal Evidence for Theories of Contagious Civil Unrest.'' Summer Institutes in Computational Social Science, University of Rochester. May 18th, 2024. 
\item ``Network Effects Panel Regression.'' Center for Political Studies, University of Michigan, November 8th, 2023.
\item ``Network Effects Panel Regression.'' Stochastic Modeling and Computational Statistics Speaker Series, Pennsylvania State University Department of Statistics, November 3rd, 2023.
\item Workshop roundtable participant, ``Lessons Learned from UNC,'' American Politics Research Group 25th Anniversary Celebration, UNC Chapel Hill, September 22nd, 2023. 
\item ``Network Event History Analysis with application to Public Policy Diffusion.'' Statistical Network Science with Applications conference, Pennsylvania State University. May 19th, 2023.
\item ``Predicting Dyadic and Geopolitical Interactions Between Spatially Moving Objects.'' Boğaziçi University (virtually), November 17th, 2021.
\item ``Attention to the COVID-19 pandemic on Twitter: Partisan differences among U.S. state legislators.'' Facebook Core Data Science, March 25th, 2021.
\item ``Network Event History Analysis for Modeling Public Policy Adoption with Latent Diffusion Networks.''  Quantitative Social Science Colloquium , Princeton University, April 12th, 2019.
\item ``Complex Dependence in Foreign Direct Investment: Network Theory and Empirical Analysis.'' Workshop on Modeling Spatial and Network Interdependence in International Relations, University of St. Gallen, December 8, 2018.
\item ``Complex Dependence in Foreign Direct Investment: Network Theory and Empirical Analysis.'' ISA Workshop on Modeling Spatial and Network Interdependence in International Relations, San Francisco, April 3, 2018.
\item ``A Network Model for Textual Communications Application to Government Email Corpora.'' Center for Statistics and the Social Sciences, University of Washington, Seattle. April 19, 2017.
\item ``Rountable on Federalism, Intergovernmental Affairs, and Public Administration.'' Midwest Political Science Association Annual Conference. April 8, 2016. 
\item ``Campaign Finance and Primary Elections.'' Meeting of the Campaign Finance Task Force, Stanford University. February, 4, 2016.
\item ``Entity Ambiguity.'' Big Data and Large Corporate Networks: Enhancing Data Quality Through Standards for the Research Community, University of Amsterdam, Amsterdam. December 15, 2015. 
\item ``Communication Network Content and Structure: A Modeling Approach with Application to Gender Mixing in Local Government Internal E-Mail Communication.'' Northeast Political Methodology Meeting, New York University, May 2, 2014.
\item ``Reflections on the Predictive Modeling of Interstate Conflict.'' ISA Working Group on Forecasting International Events, Toronto, March 25, 2014.
\item ``Inferring Policy Diffusion Networks in the American States.'' New Frontiers in Policy Diffusion Conference, University of  Iowa,  March 14-15, 2014.
\item  ``Topic-Specific Latent Space Modeling of Government Communication Networks.'' Department of Computational Social Science, George Mason University, January 15, 2014.
\item ``Inferring Policy Diffusion Networks in the American States.'' Conference on Causality in Political Networks, University of Chicago, May, 10 2013.
%\item ``Communities in Congressional Campaign Finance Networks and the Emergence of the Establishment Challenger''. Presentation for the Boston-Cambridge Colloquium on Complexity and Social Networks at the LazerLab. Northeastern University. November 29, 2012.
%\item ``Standing the Test of Time; The Breadth of Majority Coalitions and the Fate of U.S. Supreme Court Precedents.'' Conference on Judicial Collegiality, University of Southern California, Nov 11, 2011.
\end{etaremune}

\hspace{-1cm} \emph{Conference Presentations}
\begin{etaremune}

\item ``Identification and analysis of anti-globalization rhetoric by U.S. House Members.'' Annual Meeting of the Society for Political Methodology, 2023, Stanford University.
\item ``The National Network of U.S. State Legislators on Twitter,'' European Social Networks Conference, University of Greenwich, London. September 2022. 
\item ``The Network Science of Public Policy Diffusion.'' American Political Science Association Annual Meeting, Virtual, October 2021. 
\item ``The Diffusion Network Event History Model for the Study of Policy Adoption.''  American Political Science Association Annual Meeting, Washington, DC, September 2019. 
\item ``Diffusion of Candidates in Campaign Finance Networks.'' Political Networks Conference, 2018, George Mason University.
\item ``A Network Model for Textual Communications Application to Government Email Corpora.'' Annual Meeting of the Society for Political Methodology, 2017, University of Wisconsin.
\item ``Models, Methods and Network Topology: Experimental Design for the Study of Interference.'' Southern Political Science Association Annual Meeting. San Juan, PR. January 7, 2016. 
\item ``Modeling Interpersonal Government Communication Networks.'' Southern Political Science Association Annual Meeting. New Orleans, LA. January, 2015.
\end{etaremune}

\hspace{-1cm} \emph{Invited Workshops} 
\begin{etaremune}
\item Network Analysis session in the MIDAS-ICPSR Social Data Science Summer Academy (August 2024)
\item Network Analysis in Human Subjects Research (ICPSR Summer Program, 2024)
\item Machine Learning (Statistical Horizons, (December 2023, June 2024)
\item Recent Advances in Network Analysis (ICPSR Summer Program, 2023)
\item Introduction to Network Analysis (Oxfam, April 2023)
\item Introduction to Network Analysis in R (Political Network Conference, 2016--2019)
\item Network Analysis: Statistical Inference with Exponential Random Graph Models (UNC Chapel Hill, Odum Institute, May 2014)
\item TERGM: Exponential Random Graph Models for Dynamic Network Data (George Mason University, January 2014)
\item Advanced Network Analysis (ICPSR Summer Program, 2012--2015, 2018)
\item Introduction to Network Analysis (UNC Chapel Hill, Odum Institute, November 2013)
\item TERGM: Exponential Random Graph Models for Dynamic Network Data (Political Networks Conference, June 2013)
\item Advanced Bayesian Statistics (first two of four weeks) (ICPSR Summer Program, 2011)
\item Network Analysis Workshop, (The Ohio State University, May 2011)
\end{etaremune}

\section{\bf Grants}
\begin{etaremune}
\item NSF Award Number SES-2318460. ``Collaborative Research: HNDS-I: Digitally Accountable Public Representation,'' effective 09/01/2023; \$649,380.  PI with Sarah Rajtmajer and Kevin Munger, Co-PIs.
\item NSF Award Number SES- 2148215. ``Collaborative Research: Patterns, Context, and Secondary Impacts of State Policy Responses to the Pandemic,'' effective 07/01/2022; \$366,181.
\item NSF Award Number SES- 2028675. ``RAPID: Collaborative Research: The Diffusion of State Policy Responses to the 2019 Novel Coronavirus,'' effective 05/15/2020; \$16,417.
\item Institute for CyberScience Seed Grant, Pennsylvania State University,``Measuring Scalable Social Connectivity in Complex Networks of Intercity Flows,'' effective June 30, 2017 and expires June 30, 2018. Co-PI, Clio Andris. \$24,537. 
 \item NSF Award Number SES-1637089. ``RIDIR: Collaborative Research: DAPPR: Diffusion Analytics for Public Policy Research'' effective October 1, 2016 and expires September 30, 2019.  Penn State total: \$142,425.
 \item NSF Award Number SES-1558661. ``Collaborative Research: An Expanded Framework for Inferring Public Policy Diffusion Networks.'' Effective June 15, 2016 and expires May 31, 2018. Penn State total: \$178,953.
  \item Hewlett Foundation. ``Task Force Funds.'' effective October 15, 2015 and expires October 14, 2016. Penn State total: \$77,658.
 \item NSF Award Number SES-1357606. ``Collaborative Research: Specification and Estimation of Exponential Family Random Graph Models for Weighted Networks.'' effective April 15, 2014 and expires April 14, 2015.  UMass Amherst total: \$29,983.
 \item Russell Sage Foundation. ``The Revolving Door in Financial Regulation: Elite Networks and the Consequences of Unequal Access on Policymaking.'' effective January 01, 2015 and expires December 31, 2015. UMass Total: \$77,658.
 \item NSF Award Number CISE-1320219. ``Organizational Responsiveness to Open Outside Input: A Modeling Approach based on Statistical Text and Network Analysis.'' effective September 1, 2013 and expires August 31, 2016.  Co-PI with Hanna Wallach (UMass Amherst; PI). Total: \$499,326.
  \item NSF Award Number SES-1360104. ``Scientific Evidence in Regulation and Governance.'' effective May 1, 2014 and expires May 1, 2017.  PI with John Hird (UMass Amherst; Co-PI). Total: \$527,233.
\item Faculty Research Grant, University of Massachusetts Amherst Office of Research Development, 01/2013--12/2013. Total: \$14,560 
 \item Proposal Preparation Grant, University of Massachusetts Amherst College of Social and Behavioral Sciences, 01/2011--12/2011. Total:  \$10,000
 \item Research Support Grant, University of Massachusets Amherst College of Social and Behavioral Sciences, 01/2011 -- 05/2011. Total: \$4,000
\end{etaremune}

\section{\bf Awards}
\begin{etaremune}
\item 2023 Best Book Award, honorable mention, Political Networks Section of the American Political Science Association. Awarded in recognition of {\em Inferential Network Analysis}, Cambridge University Press, 2021 (co-authored with Skyler Cranmer and Jason Morgan). 
\item 2015 Jack Walker Award. Recognizes an article published in the last two calendar years that makes an outstanding contribution to research and scholarship on political organizations and parties. Awarded by the Political Organizations and Parties Section of the American Political Science Association. Co-winner with Michael Kowal and Ray La Raja for, ``The Fates of Challengers in US House Elections: The Role of Extended Party Networks in Supporting Candidates and Shaping Electoral Outcomes.''  Published in the {\em American Journal of Political Science}, 2015.
\item Best Conference Paper on Political Networks, 2013. Awarded by the Political Networks Section of the American Political Science Association. Co-winner with Jeffrey J. Harden and Frederick J. Boehmke for, ``Inferring Policy Diffusion Networks in the American States.''  Presented at the Annual Meeting of the Society for Political Methodology, University of Virginia, 2013.
\item Fellow for the Program on Computational Methods for the Social Sciences, Statistical and Applied Mathematical Sciences Institute, Fall 2013.
\end{etaremune}

\section{\bf Patents}
\begin{etaremune}
\item United States Patent; US 11,062,450 B2; Jul.13, 2021. SYSTEMS AND METHODS FOR MODELING
NEURAL ARCHITECTURE.  Skyler Cranmer, Bruce Desmarais,  Shankar Bhamidi, James Wilson,  Matthew Denny,  Zhong - Lin Lu, Paul Stillman. 
\end{etaremune}

\section{\bf Courses Taught}
\begin{etaremune}
\item Machine Learning for Political Science (Graduate: 2021, 2023)
\item Approaches and Issues in Social Data Analytics (Graduate: 2022)
\item Research Design for Social Data Analytics (Undergraduate: 2016, 2018)
\item Statistical Methods for Political Research (Graduate: 2018, 2019, 2020, 2021)
\item Political Network Analysis (Graduate: 2013, 2014, 2016, 2017, 2020)
\item Big Social Data: Approaches and Issues (Graduate: 2015, 2016, 2017)
\item Congress and the Legislative Process (Undergraduate: 2012, 2013, 2014)
\item Introduction to Quantitative Analysis (Graduate: 2012, 2014)
\item Official Secrecy in the United States, (Undergraduate: 2010, 2012) 
\end{etaremune}

%\hspace{-1cm} \emph{Thesis Committee Memberships} 

%\begin{etaremune}
%\item 
%\item Michael Kowal, UMass Amherst Political Science ABD,  2013 -- Present.
%\item James ben-Aaron, UMass Amherst Political Science ABD,  2013 -- Present.
%\item Manabu Nakashima, SUNY Albany Public Administration ABD, 2012 -- Present.
%\item Basak Taraktas, University of Pennsylvania Political Science ABD, 2014--Present.
%\item Kriste Krstovski, UMass Amherst Computer Science ABD, 2014--Present.
%\item Rachel Shorey, MS at UMass Computer Science, graduated 2012.
%\item Peter Krafft, MS at UMass Computer Science, graduated 2013.
%\item William Card, Honors Thesis, graduated 2012.
%\item Sacha Alach, Honors Thesis (awarded department of political science best thesis), graduated 2014.
%\end{etaremune}


\section{\bf Students Advised}
\vspace{.1cm}
\hspace{-1cm} \emph{Undergraduate honors thesis advisees}
\begin{etaremune} 
\item Motunrayo Bamgbose-Martins, Penn State, 2020.
\item Sascha Alach, UMass Amherst, 2014.
\end{etaremune}

\vspace{-.2cm}
\hspace{-1cm} \emph{Dissertation advisees}
\begin{etaremune}
\item Nitheesha Nakka, Penn State, PhD expected 2025.
\item Ishita Gopal, Penn State, PhD awarded 2023. Current appointment: Postdoctoral Research Associate, Transdisciplinary Institute in Applied Data Sciences, Washington University in St. Louis 
\item Sangyeon Kim, Penn State, PhD awarded 2023. Curent appointment:  Postdoctoral Researcher, Observatory on Social Media, Indiana University.
\item Taegyoon Kim, Penn State, PhD awarded 2022. Current appointment: Assistant Professor, School of Digital Humanities and Computational Social Sciences, KAIST
\item Omer Yalcin, Penn State, PhD awarded 2021. Current appointment: Faculty Fellow, Data Analytics and Computational Social Science, University of Massachusetts Amherst
\item Ted Hsuan Yun Chen, Penn State, PhD awarded 2019. Current appointment:  Assistant Professor, Department of Environmental Science and Policy, George Mason University
\item Matthew Denny, Penn State, PhD awarded 2019. Current appointment:  Staff Research Scientist, Meta
\item Fridolin Linder, Penn State, PhD awarded 2018. Current appointment: Research Scientist/Software Engineer, Meta
\item Zachary Jones, Penn State, PhD awarded 2017. Current appointment:  Senior Data Scientist, Amazon.

\end{etaremune}

\vspace{-.2cm}
\hspace{-1cm} \emph{Postdoctoral Scholars Supervised}
\begin{etaremune}
\item Isaac Pollert, 2022-present.
\item Yuehong Cassandra Tai, 2022-present.
\item Medha Uppala, 2019-2022. Current appointment: Senior Statistician, Westat.
\item Howard Liu, 2019-2020. Current appointment: Assistant Professor, Department of Political Science, University of South Carolina.

\end{etaremune}



\section{\bf External Service}
\vspace{.41cm} 
\begin{etaremune}
\item Mentor for the The Society for Political Methodology’s Expansions Initiative, Fall 2023
\item Program reviewer, Data Science program at George Washington University, March 2023
\item Program reviewer, Data Analytics program, Ohio Wesleyan University, June 2023
\item Mentor for the The Society for Political Methodology’s Expansions Initiative, Fall 2022
\item Emerging Scholar Award Committee Member, State Politics \& Policy section of the American Political Science Association, 2022
\item Host, Annual Conference on Political Networks (PolNet) 2021
\item Editorial Board Member, {\em State Politics \& Policy Quarterly},  2020 -- Present.
\item  2019--2020 Member, Christopher Z. Mooney (state politics) Dissertation Prize Selection Committee
\item 2018--2019 President, Political Networks section of the American Political Science Association.
\item Ninth Annual Conference on New Directions in Analyzing Text as Data, 2018, Program Committee Member. 
\item 2018 Best Graduate Student Poster Award Committee Chair, State Politics \& Policy Conference.
\item 2017 Best Paper Award Committee Chair, Political Organizations and Parties section of the American political Science Association.
\item Program Committee Member, European Symposium on Computational Social Science, 2017
\item Program Committee Member, International Conference on Social Informatics, 2014, 2016, 2017
\item Editorial Board Member, {\em State Politics \& Policy Quarterly},  2011 -- 2014.
\item Political Networks Conference Fellowship Committee, member 2012, chair 2013.
\item Political Networks Conference Program Committee Co-chair, 2014.
\item Program Committee Member, Workshop on Computational Social Science and the Wisdom of Crowds. Held at Neural Information Processing Systems 2011, Sierra Nevada, Spain.
\item National Science Foundation Review Panel Member, Spring 2013, Summer 2014, Spring 2021, Spring 2023.
\item Reviewer: {\em American Political Science Review, Science, American Journal of Political Science, Political Analysis, Journal of Politics, British Journal of Political Science, Conflict Management and Peace Science International Organization, International Studies Quarterly, Proceedings of the National Academy of Science,  Science,  Public Administration Review, Social Networks, State Politics \& Policy Quarterly, PLoS ONE, Policy Studies Journal, Political Research Quarterly, American Politics Research, Public Choice, Journal of Computational and Graphical Statistics, Journal of Machine Learning Research, Journal of Statistical Software, The Stata Journal, Journal of Public Policy}, National Science Foundation, Swiss National Science Foundation, National Science Center (Poland).
\item Member: American Political Science Association (sections on Political Methodology and Political Networks) and the Midwestern Political Science Association
\end{etaremune}




 % \section{\bf Awards}
 % \begin{enumerate}
% \item Flex Grant, University of Massachusetts Amherst Office of Faculty Developmemt - \$500
% \item Proposal Preparation Grant, University of Massachusetts Amherst College of Social and Behavioral Sciences - \$10,000
% \item Research Support Grant, University of Massachusets Amherst College of Social and Behavioral Sciences - \$4,000
% \end{enumerate}





%%---------------------------------------------------------------------------%%


\end{resume}

\end{document}