\documentclass[overlapped,line]{res}
\usepackage{ifpdf}
\usepackage{verbatim}
\usepackage{natbib}
\usepackage{bibentry}
\usepackage{etaremune}
%\usepackage{harvard}

\nobibliography*


%%===========================================================================%%

\begin{document}

%---------------------------------------------------------------------------
% Document Specific Customizations

% Make lists without bullets and with no indentation
\setlength{\leftmargini}{0em}
\renewcommand{\labelitemi}{}

% Use large bold font for printed name at top of pages
\renewcommand{\namefont}{\large\textbf}

% Make a nicer C++
\def\Cplusplus{C{\raise.5ex\hbox{\footnotesize ++ }}}

%---------------------------------------------------------------------------

\name{Bruce A. Desmarais~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~Curriculum Vitae}

\begin{resume}

\begin{ncolumn}{2}
  Department of Political Science       &  \texttt{bdesmarais@psu.edu}  \\
  The Pennsylvania State University  &  \texttt{brucedesmarais.com}  \\



\end{ncolumn}

%---------------------------------------------------------------------------

\section{\bf Employment}
\begin{itemize}
\item Professor of Political Science, Pennsylvania State University. 2020--Present.
\item DeGrandis-McCourtney Early Career Professor in Political Science. 2018--Present.
\item Associate Professor of Political Science, Pennsylvania State University. 2015--2020.
\item Assistant Professor of Political Science, University of Massachusetts Amherst. 2010--2015.
\end{itemize}

\section{\bf Affiliations}
\begin{itemize}
\item Associate Director, Center for Social Data Analytics, Pennsylvania State University, Fall 2018--Present
\item Director of Graduate Studies, Programs in Social Data Analytics, Pennsylvania State University, Fall 2017--Present
\item Faculty Affiliate, Pennsylvania State University Institute for Computational and Data Sciences, Fall 2015--Present.
\end{itemize}

\section{\bf Education}
\begin{itemize} 
\item Ph.D. Political Science, University of North Carolina at Chapel Hill, 2010\\
Specialties: Research Methods and American Politics
\item M.A. Political Science, University of North Carolina at Chapel Hill, 2008

\item B.A. Mathematical Economics and Public Policy, Eastern Connecticut State University, 2005,
\\ {\it Summa Cum Laude}
\end{itemize}
%---------------------------------------------------------------------------

%---------------------------------------------------------------------------

%------------------------------------------------------------------------------



%%==========================================================================

\section{\bf Recent Related Publications}
\vspace{.1cm}
%\hspace{-1cm} \emph{Books}
%\begin{etaremune}
%\item Skyler J. Cranmer, Bruce A. Desmarais, and Jason Morgan. {\em Inferential Network Analysis}. Cambridge University Press. (Under Contract)
%\end{etaremune}
%\vspace{-.1cm}
\hspace{-1cm} \emph{Book} 
\begin{etaremune}
\item \bibentry{cranmer2020inferential}
\end{etaremune}
\vspace{.1cm}
\hspace{-1cm} \emph{Journal Articles}
\begin{etaremune}
\item \bibentry{schmidPA2021}
\item \bibentry{linder2020text}
\item \bibentry{boehmke2020spid}
\item \bibentry{Scogin2019modeLLtest}
\item \bibentry{desmarais2019}
\item \bibentry{stillman2019consistent}
\item \bibentry{phadke2018}
\item \bibentry{bhamidi2018weighted}
\item \bibentry{Desmarais2018}
\item \bibentry{Bowers2018}
\item \bibentry{LeifeldJSS}

\end{etaremune}

%\newpage

\hspace{-1cm} \emph{Peer Refereed Proceedings} 
\vspace{.1cm}
\begin{etaremune}
\item \bibentry{Xu2020}
\item \bibentry{kim2020effects}
\item \bibentry{desmarais2020policy} 
\item \bibentry{Marple2017}
\item \bibentry{schmid2017}
\end{etaremune}



\bibliographystyle{plain}
\nobibliography{vitabib.bib}


\renewcommand{\labelitemi}{\bf --}



\section{\bf Related Software Projects}
\vspace{.4cm}
\begin{etaremune}
\item \bibentry{modeLLtest}
\item \bibentry{networkinference}
\item \bibentry{gergm}
\item \bibentry{xergm}
\end{etaremune}


\section{\bf Recent Related Presentations}
\vspace{.1cm}
\hspace{-1cm} \emph{Recent Invited Talks}
\begin{etaremune} 
\item ``Attention to the COVID-19 pandemic on Twitter: Partisan differences among U.S. state legislators.'' Facebook Core Data Science, March 25th, 2021.
\item ``Network Event History Analysis for Modeling Public Policy Adoption with Latent Diffusion Networks.''  Quantitative Social Science Colloquium , Princeton University, April 12th, 2019.
\item ``Complex Dependence in Foreign Direct Investment: Network Theory and Empirical Analysis.'' Workshop on Modeling Spatial and Network Interdependence in International Relations, University of St. Gallen, December 8, 2018.
\item ``Complex Dependence in Foreign Direct Investment: Network Theory and Empirical Analysis.'' ISA Workshop on Modeling Spatial and Network Interdependence in International Relations, San Francisco, April 3, 2018.
\item ``A Network Model for Textual Communications Application to Government Email Corpora.'' Center for Statistics and the Social Sciences, University of Washington, Seattle. April 19, 2017.
%\item ``Communities in Congressional Campaign Finance Networks and the Emergence of the Establishment Challenger''. Presentation for the Boston-Cambridge Colloquium on Complexity and Social Networks at the LazerLab. Northeastern University. November 29, 2012.
%\item ``Standing the Test of Time; The Breadth of Majority Coalitions and the Fate of U.S. Supreme Court Precedents.'' Conference on Judicial Collegiality, University of Southern California, Nov 11, 2011.
\end{etaremune}

\hspace{-1cm} \emph{Recent Conference Presentations}
\begin{etaremune}
\item ``Diffusion of Candidates in Campaign Finance Networks.'' Political Networks Conference, 2018, George Mason University.
\item ``A Network Model for Textual Communications Application to Government Email Corpora.'' Annual Meeting of the Society for Political Methodology, 2017, University of Wisconsin.
\item ``Models, Methods and Network Topology: Experimental Design for the Study of Interference.'' Southern Political Science Association Annual Meeting. San Juan, PR. January 7, 2016. 
\item ``Modeling Interpersonal Government Communication Networks.'' Southern Political Science Association Annual Meeting. New Orleans, LA. January, 2015.
\end{etaremune}

\hspace{-1cm} \emph{Invited Workshops} 
\begin{etaremune}
\item Advanced Network Analysis (ICPSR Summer Program, 2012--2015, 2018--2019)
\item Introduction to Network Analysis in R (Political Network Conference, 2016--2018)
\item Network Analysis: Statistical Inference with Exponential Random Graph Models (UNC Chapel Hill, Odum Institute, May 2014)
\item TERGM: Exponential Random Graph Models for Dynamic Network Data (George Mason University, January 2014)
\end{etaremune}

\section{\bf Recent Related Grants}
\begin{etaremune}

\item NSF Award Number SES- 2028675. ``RAPID: Collaborative Research: The Diffusion of State Policy Responses to the 2019 Novel Coronavirus,'' effective 05/15/2020; \$16,417.00.
 \item NSF Award Number SES-1637089. ``RIDIR: Collaborative Research: DAPPR: Diffusion Analytics for Public Policy Research'' effective October 1, 2016 and expires September 30, 2019.  Penn State total: \$142,425.
 \item NSF Award Number SES-1558661. ``Collaborative Research: An Expanded Framework for Inferring Public Policy Diffusion Networks.'' Effective June 15, 2016 and expires May 31, 2018. Penn State total: \$178,953.
 \item NSF Award Number SES-1357606. ``Collaborative Research: Specification and Estimation of Exponential Family Random Graph Models for Weighted Networks.'' effective April 15, 2014 and expires April 14, 2015.  UMass Amherst total: \$78,131.

\end{etaremune}



%\hspace{-1cm} \emph{Thesis Committee Memberships} 

%\begin{etaremune}
%\item 
%\item Michael Kowal, UMass Amherst Political Science ABD,  2013 -- Present.
%\item James ben-Aaron, UMass Amherst Political Science ABD,  2013 -- Present.
%\item Manabu Nakashima, SUNY Albany Public Administration ABD, 2012 -- Present.
%\item Basak Taraktas, University of Pennsylvania Political Science ABD, 2014--Present.
%\item Kriste Krstovski, UMass Amherst Computer Science ABD, 2014--Present.
%\item Rachel Shorey, MS at UMass Computer Science, graduated 2012.
%\item Peter Krafft, MS at UMass Computer Science, graduated 2013.
%\item William Card, Honors Thesis, graduated 2012.
%\item Sacha Alach, Honors Thesis (awarded department of political science best thesis), graduated 2014.
%\end{etaremune}

\section{\bf Recent Related Professional Service}
\vspace{.41cm} 
\begin{etaremune}
\item Host, Annual Conference on Political Networks (PolNet) 2021
\item Editorial Board Member, {\em State Politics \& Policy Quarterly},  2020 -- Present.
\item 2018--2019 President, Political Networks section of the American Political Science Association.
\item Ninth Annual Conference on New Directions in Analyzing Text as Data, 2018, Program Committee Member. 
\item Program Committee Member, International Conference on Social Informatics, 2014, 2016, 2017
\end{etaremune}




 % \section{\bf Awards}
 % \begin{enumerate}
% \item Flex Grant, University of Massachusetts Amherst Office of Faculty Developmemt - \$500
% \item Proposal Preparation Grant, University of Massachusetts Amherst College of Social and Behavioral Sciences - \$10,000
% \item Research Support Grant, University of Massachusets Amherst College of Social and Behavioral Sciences - \$4,000
% \end{enumerate}





%%---------------------------------------------------------------------------%%


\end{resume}

\end{document}