\documentclass[overlapped,line]{res}
\usepackage{ifpdf}
\usepackage{verbatim}
\usepackage{natbib}
\usepackage{bibentry}
\usepackage{etaremune}
%\usepackage{harvard}

\nobibliography*


%%===========================================================================%%

\begin{document}

%---------------------------------------------------------------------------
% Document Specific Customizations

% Make lists without bullets and with no indentation
\setlength{\leftmargini}{0em}
\renewcommand{\labelitemi}{}

% Use large bold font for printed name at top of pages
\renewcommand{\namefont}{\large\textbf}

% Make a nicer C++
\def\Cplusplus{C{\raise.5ex\hbox{\footnotesize ++ }}}

%---------------------------------------------------------------------------

\name{Bruce A. Desmarais~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~Curriculum Vitae}

\begin{resume}

\begin{ncolumn}{2}
  Department of Political Science       &  \texttt{bdesmarais@psu.edu}  \\
  Pennsylvania State University  &  \texttt{brucedesmarais.com}  \\
  321 Pond Lab    & \texttt{publons.com/a/1369768/} \\ 
University Park, PA 16802 &  \texttt{orcid.org/0000-0002-3031-8883} \\
 Phone: (814)863-8346  & \url{twitter.com/brucedesmarais}   \\  



\end{ncolumn}

%---------------------------------------------------------------------------

\section{\bf Employment}
\begin{itemize}
\item Research Scientist, Core Data Science, Meta Platforms (Spring 2022, on sabbatical).
\item Professor of Political Science, Pennsylvania State University. 2020--Present.
\item DeGrandis-McCourtney Early Career Professor in Political Science. 2018--Present.
\item Associate Professor of Political Science, Pennsylvania State University. 2015--2020.
\item Assistant Professor of Political Science, University of Massachusetts Amherst. 2010--2015.
\end{itemize}

\section{\bf Affiliations}
\begin{itemize}
\item Associate Director, Center for Social Data Analytics, Pennsylvania State University, Fall 2018--Present
\item Director of Graduate Studies, Programs in Social Data Analytics, Pennsylvania State University, Fall 2017--Present
\item Faculty Affiliate, Pennsylvania State University Institute for Computational and Data Sciences, Fall 2015--Present.
\end{itemize}

\section{\bf Education}
\begin{itemize} 
\item Ph.D. Political Science, University of North Carolina at Chapel Hill, 2010\\
Specialties: Research Methods and American Politics
\item M.A. Political Science, University of North Carolina at Chapel Hill, 2008

\item B.A. Mathematical Economics and Public Policy, Eastern Connecticut State University, 2005,
\\ {\it Summa Cum Laude}
\end{itemize}
%---------------------------------------------------------------------------

%---------------------------------------------------------------------------

%------------------------------------------------------------------------------



%%==========================================================================

\section{\bf Publications}
\vspace{.1cm}
%\hspace{-1cm} \emph{Books}
%\begin{etaremune}
%\item Skyler J. Cranmer, Bruce A. Desmarais, and Jason Morgan. {\em Inferential Network Analysis}. Cambridge University Press. (Under Contract)
%\end{etaremune}
%\vspace{-.1cm}
\hspace{-1cm} \emph{Book} 
\begin{etaremune}
\item \bibentry{cranmer2020inferential}
\end{etaremune}
\vspace{.1cm}
\hspace{-1cm} \emph{Journal Articles (2019-present)}
\begin{etaremune}
\item \bibentry{KimPSRM}
\item \bibentry{KimLSQ}
\item \bibentry{NeumannJITP}
\item \bibentry{schmidPA2021}
\item \bibentry{schoeneman_zhu_desmarais_2020}
\item \bibentry{linder2020text}
\item \bibentry{boehmke2020spid}
\item \bibentry{cranmer2020contagion}
\item \bibentry{liu2019migration}
\item \bibentry{Scogin2019modeLLtest}
\item \bibentry{desmarais2019}
\item \bibentry{stillman2019consistent}
\item \bibentry{bergner}
\item \bibentry{phadke2018}
\item \bibentry{costa2019public}
\end{etaremune}

%\newpage



\bibliographystyle{plain}
\nobibliography{vitabib.bib}


\renewcommand{\labelitemi}{\bf --}







\section{\bf Grants (2019-Present)} 
\begin{etaremune}
\item NSF Award Number SES- 2148215. ``Collaborative Research: Patterns, Context, and Secondary Impacts of State Policy Responses to the Pandemic,'' effective 07/01/2022; \$366,181.
\item NSF Award Number SES- 2028675. ``RAPID: Collaborative Research: The Diffusion of State Policy Responses to the 2019 Novel Coronavirus,'' effective 05/15/2020; \$16,417.
\end{etaremune}



\section{\bf Courses Taught}
\begin{etaremune}
\item Machine Learning for Political Science (Graduate: 2021)
\item Research Design for Social Data Analytics (Undergraduate: 2016, 2018)
\item Statistical Methods for Political Research (Graduate: 2018, 2019, 2020, 2021)
\item Political Network Analysis (Graduate: 2013, 2014, 2016, 2017, 2020)
\item Approaches and Issues in Social Data Analytics (Graduate: 2015, 2016, 2017)
\item Congress and the Legislative Process (Undergraduate: 2012, 2013, 2014)
\item Introduction to Quantitative Analysis (Graduate: 2012, 2014)
\item Official Secrecy in the United States, (Undergraduate: 2010, 2012) 
\end{etaremune}

%\hspace{-1cm} \emph{Thesis Committee Memberships} 

%\begin{etaremune}
%\item 
%\item Michael Kowal, UMass Amherst Political Science ABD,  2013 -- Present.
%\item James ben-Aaron, UMass Amherst Political Science ABD,  2013 -- Present.
%\item Manabu Nakashima, SUNY Albany Public Administration ABD, 2012 -- Present.
%\item Basak Taraktas, University of Pennsylvania Political Science ABD, 2014--Present.
%\item Kriste Krstovski, UMass Amherst Computer Science ABD, 2014--Present.
%\item Rachel Shorey, MS at UMass Computer Science, graduated 2012.
%\item Peter Krafft, MS at UMass Computer Science, graduated 2013.
%\item William Card, Honors Thesis, graduated 2012.
%\item Sacha Alach, Honors Thesis (awarded department of political science best thesis), graduated 2014.
%\end{etaremune}






 % \section{\bf Awards}
 % \begin{enumerate}
% \item Flex Grant, University of Massachusetts Amherst Office of Faculty Developmemt - \$500
% \item Proposal Preparation Grant, University of Massachusetts Amherst College of Social and Behavioral Sciences - \$10,000
% \item Research Support Grant, University of Massachusets Amherst College of Social and Behavioral Sciences - \$4,000
% \end{enumerate}





%%---------------------------------------------------------------------------%%


\end{resume}

\end{document}